My title

### 2024-04-12 paper/paper.qmd
feature engineering finished

```{r}
#| echo: false
#| warning: false
#| message: false
#| label: tbl-model1variables
#| tbl-cap: First lasso regression model important variables

@@

# View the important predictors
important_predictors |>
  select(-penalty) |>
  rename(
    "Predictors" = term,
    "Coefficients" = estimate
  ) |>
  kable(booktabs = TRUE, digits = 2)
```

>>>>

```{r}
#| echo: false
#| warning: false
#| message: false
#| label: tbl-model1variables
#| tbl-cap: Top 5 important variables of the first lasso regression model

@@

# View the important predictors
important_predictors |>
  head(5) |>
  select(-penalty) |>
  rename(
    "Predictors" = term,
    "Coefficients" = estimate
  ) |>
  kable(booktabs = TRUE, digits = 2)
```

@tbl-modelvariables lists the predictors with the highest magnitude coefficients from the lasso regression model, indicating their relative importance in predicting the outcome variable. The listed predictors are minutes played ('mp'), turnovers ('tov'), defensive rebounds ('drb'), offensive rebounds ('orb'), and personal fouls ('pf'), with their corresponding coefficients.

Minutes Played (310.86): The positive coefficient suggests a strong positive relationship between the number of minutes a player plays and their point total. More minutes played typically allows more opportunities to score points. Turnovers (225.98): The positive coefficient here is interesting as turnovers are generally negative events. However, it might indicate that players who are more involved in the game (and therefore more likely to score points) also have more turnovers. Defensive Rebounds (73.62): A positive coefficient for defensive rebounds implies players who gather more rebounds on the defensive end also tend to score more points, possibly due to the additional possessions they secure for their team. Offensive Rebounds (-70.80): The negative coefficient for offensive rebounds suggests that players who get more offensive rebounds do not necessarily score more points. This could reflect a role specialization where some players focus on rebounding rather than scoring. Personal Fouls (-65.66): The negative coefficient indicates that players who commit more fouls tend to score fewer points. This could be because committing fouls may limit a player's time on the court due to foul trouble.
